---
title: "cleanup rush data"
author: "ryan schubert"
date: "10/19/2022"
output: html_document
---

```{r setup, include=FALSE}
"%&%" = function(a,b) paste0(a,b)
```


#data harmonization
#sometimes data is ill formatted in between sets of data
#for example a date may be a "character" in one set of data and a "Date" object in another
#to this end it is necessary to preprocess data so that they are harmonic

here rush's dates are poorly formatted so this is to clean them

```{r}
in.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/original/Rush/"
out.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/processedData/dashboardData/Rush/"
iterables<-list.files(in.dir)
iterables<-iterables[!grepl('archive',iterables) & !grepl('Icon',iterables)]
for ( i in 1:length(iterables)) {
  rushdata<-fread(in.dir %&% iterables[i])
  index<-which(grepl("date",colnames(rushdata),ignore.case=T))
  updated<-rushdata[,..index] %>% lapply(.,as.Date,format = "%m/%d/%Y")
  rushdata[,index]<-updated
  if(grepl('patient',iterables[i])) {
    rushdata <- rushdata %>% mutate(ZIP_CODE=as.integer(ZIP_CODE))
  }
  fwrite(rushdata,out.dir %&% iterables[i])
}

```
Rush's zip codes are also poorly formatted so we will coerce it to numeric

```{r}
data<-fread("/Users/ryanschubert/Dropbox (Rush)/WCN Data/processedData/dashboardData/Rush/patient_data_202211.txt"   )
str(data$ZIP_CODE)
```

UCLA's visits data has an extra field so we will strip that out

```{r}
in.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/original/UCLA/202212/"
out.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/processedData/dashboardData/UCLA/"
targetFile<-list.files(in.dir)[grepl('^visit',list.files(in.dir))]
UCLAnames<-colnames(fread(in.dir %&% targetFile,nrow=1,header=T))
UCLAraw<-fread(in.dir %&% targetFile,skip=1)
UCLAraw<-UCLAraw %>% select(-V18)
colnames(UCLAraw)<-UCLAnames[1:17]
fwrite(UCLAraw,out.dir %&% targetFile)

```

UCLA also has an extra field in their referral datasets

```{r}
in.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/original/UCLA/202212/"
out.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/processedData/dashboardData/UCLA/"
targetFile<-list.files(in.dir)[grepl('^referral',list.files(in.dir))]
UCLAraw<-fread(in.dir %&% targetFile) %>% select(-V11)
fwrite(UCLAraw,out.dir %&% targetFile)
```

EMORY -> 6404fd27e7b6f19f60add56c06909a8a0f81b877a49b480c34ecae3a3dcb32d6-E1IO1-P-0-0 has duplicate entries in assessments

```{r}

in.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/original/EMORY/"
out.dir<-"/Users/ryanschubert/Dropbox (Rush)/WCN Data/processedData/dashboardData/UCLA/"
```

