---
title: "debug fiscal quarters determination"
author: "ryan schubert"
date: "10/25/2022"
output: html_document
---
```{r}

```


## pseudocode 

we need to somehow determine fiscal quarters, 
both to set the correct boundaries for fiscal quarters and to return the correct fiscal quarters

what we can do is check the current date
the current date should tell you what the current fiscal quarter is
it should also tell you which fiscal quarters you must return

###determining fiscal quarters (logic from KPI document)

WWP Fiscal Year: October through September
o	The 1 quarter will only drop off the report once there are 4 full quarters of data to report. This means that until data for all 3 months in the most recent quarter is available there will be a 5th quarter on the report showing partial data for that quarter
By WWP fiscal year quarter 
	FY Q1 = Oct – Dec
	FY Q2 = Jan – Mar
	FY Q3 = Apr – Jun
	FY Q4 = Jul - Sep


#first check date
  determine year,
  current fiscal year,
  current fiscal quarter
  previous 4 fiscal quarters

which quarter you are in is easily determined as the year is actually arbitrary - the quarter is solely determined my the month

similarly fiscal year can also be determined 

```{r}
library(lubridate)
"%&%" = function(a,b) paste0(a,b)
today<-Sys.Date()

determineFiscalYear<-function(date){
  year<-as.numeric(format(as.Date(date), '%Y'))
  FY<-ifelse(date >= year %&% "-10-01",(year + 1),year)
  return(FY)
}

determineQuarter=function(date) {
  year<-as.numeric(format(as.Date(date), '%Y'))
  quarter<-case_when(date >= year %&% "-10-01" ~ (year + 1) %&% "-Q1",
                     date >= year %&% "-07-01" ~ year %&% "-Q4", 
                     date >= year %&% "-04-01" ~ year %&% "-Q3",
                     date >= year %&% "-01-01" ~ year %&% "-Q2")
  return(quarter)
}

determineQuarterStart<-function(date){
  year<-as.numeric(format(date, '%Y'))
  quarter<-case_when(date >= year %&% "-10-01" ~ year %&% "-10-01",
                     date >= year %&% "-07-01" ~ year %&% "-07-01",
                     date >= year %&% "-04-01" ~ year %&% "-04-01",
                     date >= year %&% "-01-01" ~ year %&% "-01-01")
  return(quarter)
}

createQuarterTemplate<-function(date) {
  template<-data.frame(startDates=rep(NA,5),
                       quarter=rep(NA,5))
  iterDate<-today
  for(i in 1:5) {
    template$startDates[i]<-determineQuarterStart(iterDate)
    iterDate<-iterDate %m-% months(3)
    template$quarter[i]<-determineQuarter(template$startDates[i])
  }
 return(template)
}




```



```{r}

```